---
title: "Assessment 4"
output: statsr:::statswithr_lab
author: Jacob John
---

<div id="instructions">
Complete all **Exercises**, and submit answers to **VtopBeta**
</div>

## Datasets

```{r}
### load packages
library(caret)
library(knitr)
```

```{r echo = FALSE, results = 'asis'}

kable(iris[1:5,1:5], caption = "Iris dataset for training and testing")

```

## Split it into training set and testing set and validation set

```{r data, message = FALSE}
ir_data=iris
set.seed(100)
head(ir_data)
intrain <- createDataPartition(y = ir_data$Species, p= 0.7, list = FALSE)
training<-iris[intrain,]
testing<-ir_data[-intrain,]
dim(training);dim(testing)
summary(ir_data)
training[["Species"]] = factor(training[["Species"]])
trctrl <- trainControl(method = "repeatedcv", number = 10, repeats = 3)
```

The results of confusion matrix show that this time the accuracy on the test set is __95.56%__.

## using e1071
```{r naive, message = FALSE}
library(e1071)
model <- naiveBayes(Species ~., data = training)
class(model)
summary(model)
print(model)
preds <- predict(model, newdata = training)
table(preds,training$Species)
(35+33+32)/(35+33+2+32+3)#change this according to the diagonal element of the previous statement result 
```

Accuracy is __95.2381%__.

## Using mlbench
```{r}
library(mlbench)
data("HouseVotes84")
data(HouseVotes84, package = "mlbench")
model <- naiveBayes(Class ~ ., data = HouseVotes84)
predict(model, HouseVotes84[1:10,])
predict(model, HouseVotes84[1:10,], type = "raw")
pred <- predict(model, HouseVotes84)
table(pred, HouseVotes84$Class)
(238+155)/(238+155+29+13)
```

Accuracy is __90.34483%__.

```{r}
## using laplace smoothing:
model <- naiveBayes(Class ~ ., data = HouseVotes84, laplace = 3)
pred <- predict(model, HouseVotes84[,-1])
table(pred, HouseVotes84$Class)
(237+156)/(237+156+12+30)
```

Accuracy is still __90.34483%__.

## Using a contingency table
```{r}
data(Titanic)
m <- naiveBayes(Survived ~ ., data = Titanic)
m
predict(m, as.data.frame(Titanic))
```

## Cervical Cancer
```{r}
cancer <- read.csv("risk_factors_cervical_cancer.csv")
cancer[cancer=='?'] <- NA
cancer[["Dx.Cancer"]] = factor(cancer[["Dx.Cancer"]],ordered = TRUE)

#Splitting Dataset
intrain <- createDataPartition(y = cancer$Dx.Cancer, p = 0.7, list = FALSE)
training<-cancer[intrain,]
testing<-cancer[-intrain,]
dim(training);dim(testing)
summary(cancer)
trctrl <- trainControl(method = "repeatedcv", number = 2, repeats = 3)

#Training Model
model <- naiveBayes(Dx.Cancer ~ ., data = training)
class(model)
summary(model)
print(model)

#Testing Model
preds <- predict(model, newdata = testing)

#Confusion Matrix
conmat <- table(preds,testing$Dx.Cancer)

#Accuracy
accuracy <- (conmat[1]+conmat[4])/(conmat[1]+conmat[2]+conmat[3]+conmat[4])*100
accuracy

#ROC
library(pROC)
library(rowr)
prediction <- rev(seq_along(cancer$Dx.Cancer))
prediction[1:len(preds)] <- mean(as.numeric(preds))
roc_obj <- roc(cancer$Dx.Cancer,prediction)
auc(roc_obj)
```

## Sentiment Analysis of Movie Reviews
```{r}
# Load additional libraries
library(tm)
library(RTextTools)
library(dplyr)
# Library for parallel processing
library(doMC)
registerDoMC(cores=detectCores())  # Use all available cores
```

### Reading the data
```{r}
df<- read.csv("movie-pang02.csv", stringsAsFactors = FALSE)
glimpse(df)
# Randomize the dataset
set.seed(1)
df <- df[sample(nrow(df)), ]
df <- df[sample(nrow(df)), ]
glimpse(df)
# Convert the 'class' variable from character to factor.
df$class <- as.factor(df$class)
```

### Bag of Words Tokenisation
```{r}
corpus <- Corpus(VectorSource(df$text))
corpus
inspect(corpus[1:3])
```

### Data Cleanup
```{r}
# Use dplyr's  %>% (pipe) utility to do this neatly.
corpus.clean <- corpus %>%
  tm_map(content_transformer(tolower)) %>% 
  tm_map(removePunctuation) %>%
  tm_map(removeNumbers) %>%
  tm_map(removeWords, stopwords(kind="en")) %>%
  tm_map(stripWhitespace)
```

### Document Term Matrix
```{r}
dtm <- DocumentTermMatrix(corpus.clean)
inspect(dtm[40:50, 10:15])
```

### Paritioning
```{r}
df.train <- df[1:1500,]
df.test <- df[1501:2000,]

dtm.train <- dtm[1:1500,]
dtm.test <- dtm[1501:2000,]

corpus.clean.train <- corpus.clean[1:1500]
corpus.clean.test <- corpus.clean[1501:2000]
```

### Feature set selection
```{r}
dim(dtm.train)
fivefreq <- findFreqTerms(dtm.train, 5)
length((fivefreq))

# Use only 5 most frequent words (fivefreq) to build the DTM
dtm.train.nb <- DocumentTermMatrix(corpus.clean.train, control=list(dictionary = fivefreq))
dim(dtm.train.nb)
dtm.test.nb <- DocumentTermMatrix(corpus.clean.test, control=list(dictionary = fivefreq))
dim(dtm.train.nb)
```

### Boolean feature Multinomial Naive Bayes
```{r}
# Function to convert the word frequencies to yes (presence) and no (absence) labels
convert_count <- function(x) {
  y <- ifelse(x > 0, 1,0)
  y <- factor(y, levels=c(0,1), labels=c("No", "Yes"))
  y
}

# Apply the convert_count function to get final training and testing DTMs
trainNB <- apply(dtm.train.nb, 2, convert_count)
testNB <- apply(dtm.test.nb, 2, convert_count)

# Train the classifier
system.time( classifier <- naiveBayes(trainNB, df.train$class, laplace = 1) )

# Use the NB classifier we built to make predictions on the test set.
system.time( pred <- predict(classifier, newdata=testNB) )

# Create a truth table by tabulating the predicted class labels with the actual class labels 
table("Predictions"= pred,  "Actual" = df.test$class )
```

### Confusion Matrix
```{r}
conf.mat <- confusionMatrix(pred, df.test$class)
conf.mat
conf.mat$byClass
conf.mat$overall
# Prediction Accuracy
conf.mat$overall['Accuracy']
```

## Apriori
```{r}
library(arules)
#Data Preprocessing
load("dataset.RData")
summary(dataset)
itemFrequencyPlot(dataset,topN=10)
#Apriori
rules <- apriori(data=dataset,parameter=list(support=0.60,confidence=0.80))
summary(rules)
#Data Visualization
inspect(sort(rules,by='lift')[1:10])

```

## K-means
```{r}
library(ggplot2)
set.seed(20)
irisCluster <- kmeans(iris[,3:4],3,nstart=20)
irisCluster
#Comparing clusters with the species
table(irisCluster$cluster, iris$Species)
irisCluster$cluster <- as.factor(irisCluster$cluster)
ggplot(iris, aes(Petal.Length, Petal.Width, color = irisCluster$cluster)) + geom_point()

```